\documentclass[journal]{IEEEtran}

% Short version (target: 8 pages, IEEE Transactions on Education). This is a condensed
% companion to the full paper in ../latex/ -- see SHORT_VERSION.md in this directory for what
% was cut and why. The two are maintained as separate files (not a single \ifshort-toggled
% source) since the cuts are too extensive (roughly half the content) for conditional
% inclusion to stay readable; changes made to the long version after this split need to be
% manually ported here if they should also apply to the short one.

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\graphicspath{{../latex/figures/}}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{tikz}
\usetikzlibrary{positioning, arrows.meta, fit, backgrounds}
\usepackage{cite}
\usepackage{hyperref}

% TODO before submission: fill in department names, e-mail addresses, and (if applicable)
% IEEE membership grades (e.g. \IEEEmembership{Senior Member, IEEE}) for each author below --
% left as plain names/affiliations here since none of this was supplied and it should not be
% guessed at. Kept identical to the long version's author block.
\title{CircuitCraft: An Open-Source Minecraft Mod to Teach Analog Circuit Theory using a Real Nodal Analysis Solver}

\author{Rodrigo~Picos, Stavros~G.~Stavrinides, George~Stavrinides, Ariadna~Picos, and~Gerard~Picos%
\thanks{R. Picos, A. Picos, and G. Picos are with the Universitat de les Illes Balears, Palma, Spain.}%
\thanks{S. G. Stavrinides and G. Stavrinides are with the Democritus University of Thrace, Xanthi, Greece.}%
\thanks{Manuscript received XX Month 2026; revised XX Month 2026.}}

\begin{document}
\maketitle

\begin{abstract}
This paper presents CircuitCraft, an open-source modification (``mod'') for the sandbox
game Minecraft that transforms the game world into an analog electronics laboratory. Players
place resistor, capacitor, inductor, memristor, diode, and ideal op-amp blocks, wire them
together using conductive blocks, drive them with DC and time-varying sources, and probe the
resulting voltages and currents with a pair of handheld oscilloscope probes -- one
time-domain, one X-Y -- all rendered as ordinary game objects placed and manipulated with the
same mechanics used to construct anything else within the game. In contrast to scripted or
table-driven approximations of circuit behavior, every electrical quantity in CircuitCraft
is produced by a genuine modified nodal analysis (MNA) solver of the kind
employed in SPICE-family simulators, including a charge-controlled linear-drift memristor
model, a linearized diode, and an ideal op-amp modeled as a nullor. A separate, complex-valued
small-signal (AC) solver, sharing the same wiring topology, additionally lets a player sweep a
dedicated AC source across a configurable frequency range and read the result as a Bode plot.
This paper summarizes the mod's software architecture, the circuit-theoretic design decisions
underlying it, the pedagogical rationale for embedding a correct solver within a game
environment rather than a dedicated simulator, and two representative worked experiments; an
extended version with all six worked experiments, full crafting-recipe tables, and additional
architectural detail is available alongside the mod's source code.
\end{abstract}

\begin{IEEEkeywords}
Minecraft, serious games, game-based learning, circuit simulation, modified nodal analysis,
SPICE, memristor, analog electronics, engineering education.
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\input{sections/01_introduction}
\input{sections/02_related_work}
\input{sections/03_minecraft_mechanics}
\input{sections/04_architecture}
\input{sections/05_circuit_solver}
\input{sections/05c_ac_analysis}
\input{sections/06_pedagogy}
\input{sections/06b_experiments}
\input{sections/07_validation}
\input{sections/08_limitations_future_work}
\input{sections/09_conclusion}
\input{sections/10_availability}

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
