\section{Introduction}
\label{sec:introduction}

Teaching the transient and steady-state behavior of analog circuits is difficult in part
because the underlying phenomena -- charge accumulating on a capacitor plate, flux linking
an inductor's turns, a memristor's internal state drifting with the integral of the current
through it -- are not directly observable. Students must reason about quantities they cannot
see, using differential equations whose solutions they are frequently encountering for the
first time in the same course. The conventional response is to pair the mathematics with a
laboratory bench and, increasingly, with software simulators such as SPICE~\cite{nagel1973spice},
LTspice, or browser-based tools such as the Falstad circuit simulator and PhET's Circuit
Construction Kit. These tools are effective, but each presents the circuit as a schematic on
a two-dimensional canvas, an abstraction removed by one level from the physical act of
connecting components that a breadboard or benchtop still preserves.

Sandbox games occupy a distinctive position relative to both approaches. Minecraft in
particular has an established record as an informal STEM learning environment
(Section~\ref{sec:related-work}), in part because constructing something inside it -- a
redstone logic circuit, a working calculator, a piston-driven elevator -- requires systems
thinking comparable to an engineering task while remaining playful and low
stakes~\cite{nebel2016mining}. Minecraft's own redstone subsystem is already a widely used
entry point into digital logic, examined further in Section~\ref{sec:minecraft-mechanics}.
No equivalent exists, however, for \emph{analog} circuit theory within the base game:
redstone signals are effectively boolean, propagated through a discrete per-block delay
rather than continuously, with no built-in notion of voltage, current, capacitance, or
continuous time.

This paper describes CircuitCraft~\cite{picos2026circuitcraft}, a modification
(``mod'') for the Fabric mod loader, released as free and open-source software under the MIT
license, that adds a complete set of analog circuit components to Minecraft: resistors,
capacitors, inductors, memristors, diodes, an ideal operational amplifier, DC and
time-varying voltage sources, a dedicated AC (small-signal) source, an ammeter, wire, an
explicit ground-reference block, and three handheld oscilloscope probes -- a multi-channel
time-domain probe, an X-Y probe plotting one pinned signal against another, and a Bode-plot
probe sweeping the AC source across a configurable frequency range. Placing and wiring these blocks
together constructs an actual circuit topology within the game world; a modified nodal
analysis solver, structurally identical to the technique used by SPICE-family
simulators~\cite{ho1975mna}, is re-solved once per game tick (20~Hz) to drive every block's
displayed voltage, current, and internal state. No behavior in the mod is a scripted
approximation of the underlying physics: an RC charging curve resembles an RC charging curve
because the underlying linear system is actually solved, a diode's current follows the same
linearized Shockley relation~\cite{shockley1949diode} a SPICE-family simulator would use, and
a memristor's resistance drifts according to the same charge-controlled ordinary differential
equation used in the original HP linear-drift model~\cite{strukov2008missing}, rather than a
lookup table tuned to appear plausible.

The remainder of this paper is organized as follows. Section~\ref{sec:related-work}
situates CircuitCraft relative to existing circuit simulators, the literature on
Minecraft in education, and the memristor-modeling literature. Section~\ref{sec:minecraft-mechanics}
examines, in greater depth, which of Minecraft's own construction mechanics -- block
placement and orientation, the native redstone subsystem, and the modding platform's
block-entity and tick-loop primitives -- the mod builds upon, and why redstone's existing
role as an entry point into digital logic does not, by itself, extend to analog circuit
theory. Section~\ref{sec:architecture} describes the mod's own software architecture, in
particular the topology-construction algorithm used to translate a player's in-world wiring
into a circuit graph. Section~\ref{sec:circuit-solver} describes the solver itself,
including the explicit, player-placeable ground reference that allows the notion of
``ground'' to be taught rather than assumed. Section~\ref{sec:control-network} describes a
second, independent network, unrelated to the electrical topology, by which a voltage or
frequency module propagates a shared amplitude or frequency setting to one or more function
generators. Section~\ref{sec:ac-analysis} describes a second, complex-valued solver used for
AC (small-signal) analysis, including a two-pole frequency-dependent gain model for the
op-amp and the Bode-plot probe that sweeps a dedicated AC source across a configurable
frequency range. Section~\ref{sec:pedagogy} discusses the
pedagogical rationale underlying each design choice, and Section~\ref{sec:experiments} gives
five complete, reproducible worked circuits -- a voltage divider, an RC and an RLC step
response, a diode rectifier, and a memristor hysteresis-loop measurement -- built directly
into the same world, with exact preset values and closed-form expected results for each.
Section~\ref{sec:validation} describes
how the solver and the surrounding game logic were verified during development.
Section~\ref{sec:limitations} discusses current limitations and planned classroom
evaluation, and Section~\ref{sec:conclusion} concludes.
