\section{Limitations and Future Work}
\label{sec:limitations}

\textbf{Reactive state resets on topology change.} The circuit for an entire network is
rebuilt from scratch whenever its wiring changes anywhere within that network, which resets
a capacitor's stored charge or an inductor's current to zero at that instant. The memristor
is deliberately exempted, since persistent state is its central pedagogical purpose, but a
student who extends a circuit while a capacitor is mid-charge, for example, will observe
that capacitor's voltage reset rather than continue from its prior value. Carrying reactive
state across a topology rebuild in the same manner the memristor's state is carried is
planned future work and is primarily a bookkeeping problem: the new topology's node indices
must be matched to the element's previous node indices before its stored voltage or current
can be meaningfully re-applied.

\textbf{Discrete presets remain the default interaction, alongside an optional numeric
entry.} Every adjustable quantity -- a resistor's resistance, a source's amplitude or
frequency, the memristor's $R_{on}$, $R_{off}$, and switching-charge parameters -- is still,
by default, one of a small number of discrete presets cycled by an empty-hand right-click,
preserving the interaction model this paper's own worked experiments
(Section~\ref{sec:experiments}) rely on. A shift-right-click now additionally opens a
text-entry screen, in the same interaction spirit as editing a sign, letting a player type
any value directly rather than only stepping through the fixed cycle; the screen clamps
entry to the same $[\min,\max]$ range the existing preset cycle already spans for that
quantity; the server independently re-clamps whatever value it receives, rather than trusting
the client's own display-side clamping. This does not yet extend to every adjustable
quantity in the mod (the diode's silicon/germanium/LED family and the function generator's
waveform shape remain categorical presets with no single underlying numeric value to type),
and the interaction itself -- typing into a floating on-screen box while looking at the
block -- is a more conventional GUI paradigm than the rest of the mod's otherwise
purely block-placement-driven interface, a design tension future work could revisit.

\textbf{AC analysis is small-signal only, with fixed op-amp pole values.} The AC solver
(Section~\ref{sec:ac-analysis}) always stamps every independent source other than the pinned
AC Source at exactly 0~V, regardless of a power supply's or function generator's own
redstone-activated state -- the standard small-signal convention, but one that does not
distinguish a source that is genuinely switched off from one merely treated as an AC ground
for the sweep. The two-pole op-amp model's gain, and both pole frequencies, are fixed
constants rather than exposed as an editable preset the way every other adjustable quantity
in the mod now is (Section~\ref{sec:limitations}'s discussion of the value editor above);
exposing them would let a player explore how moving a dominant pole changes phase margin
directly, rather than only observing one fixed, illustrative op-amp's response. The
memristor's AC case is, as noted in Section~\ref{sec:ac-analysis}, simply a frozen resistor
with no frequency dependence of its own -- a real small-signal memristor model remains
future work.

\textbf{Solver scalability.} The MNA system for each independent network is solved by dense
Gaussian elimination every tick, which is adequate for the circuit sizes a single player
typically constructs by hand, but scales as $O(n^3)$ in the number of independent nodes and
does not exploit the sparsity that a large circuit's conductance matrix would in practice
possess. A sparse solver, or amortization of re-solves across ticks when no electrically
relevant change has occurred, would be necessary before the tool could comfortably support
very large student-built circuits, or a heavily populated multiplayer server hosting
numerous independent networks simultaneously.

\textbf{Verification remains informal.} As noted in Section~\ref{sec:validation}, the
closed-form comparisons used during development have not yet been captured as a persisted,
automatically re-run regression suite, and the tool's pedagogical effectiveness has to date
been assessed only informally by its author, rather than through a controlled classroom
study. A natural next step is a pre/post evaluation using an established circuits concept
inventory, comparing a cohort using CircuitCraft as a supplementary laboratory activity
against a cohort using a conventional schematic-based simulator, in order to test whether
the game-based, first-person construction experience described in Section~\ref{sec:pedagogy}
produces a measurable difference in conceptual understanding, rather than in engagement
alone.

\textbf{Memristor model fidelity.} As discussed in Section~\ref{sec:related-work}, the mod
implements only the original HP linear-drift formulation, which is known to exhibit boundary
pinning under sustained excitation, a limitation subsequent compact models such as Biolek et
al.'s windowed variant~\cite{biolek2009spice} were specifically designed to address. Exposing
one or more alternative compact models as an additional preset would allow the tool to also
illustrate why the modeling literature moved beyond the original formulation, rather than
presenting it as the final word on memristor behavior.

\textbf{Platform dependency.} The mod is necessarily tied to a specific version of
Minecraft and of the Fabric mod loader, both of which are externally maintained and continue
to evolve; Section~\ref{sec:validation} discusses the verification discipline this
requires, but ongoing maintenance to track future game updates remains an unavoidable cost
of building instructional software atop an actively developed commercial platform, rather
than a purpose-built, stable simulator.
